---
title: "p8105_hw1_zz2780"
output: github_document
date: "2022-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(ggplot2)
```

Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```

This data includes the species, year (2007-2009), and sex of penguins and island they live in. It also includes each penguin's bill length (mm), bill depth (mm), flipper length (mm), and body mass (g).

The data has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm=TRUE)` mm.

Code for mean flipper length
```{r}
mean(penguins$flipper_length_mm, na.rm=TRUE)
```
Scatterplot of flipper length and bill length
```{r}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species))+geom_point()
ggsave("scatter_plot.pdf", height=4, width=6)
```

Problem 2
```{r}
df1 = tibble(
  a=rnorm(10),
  b=a>0,
  c = c("AA","BB","CC","DD","EE","FF","GG","HH","II","JJ"),
  d= factor(c("MID", "HIGH", "LOW", "LOW", "HIGH", "MID", "MID", "HIGH", "LOW", "MID"))
)
```

Mean of each variable
```{r}
#Mean of numeric variable
mean(df1$a)
#Mean of logical variable
mean(df1$b)
#Mean of character variable
mean(df1$c)
#Mean of factor variable
mean(df1$d)
```
It works when I tried to take the mean of a numeric variable and the mean of a logical variable. 

It returns NA value when I tried to take the mean of a character variable and a factor variable.

Change to numeric variable
```{r}
#logical variable
as.numeric(df1$b)
#character variable
as.numeric(df1$c)
#factor variable
as.numeric(df1$d)
```

The logical variable changes to string with values of 1 and 0, with True being 1 and False being 0. This explains why the logical variable has a numeric mean whey I tried to take one.

The character variable becomes a string of NA value, with the error "NA's introduced by coercion". This explains that why the character variable does not have a mean when I tried to take one.

The factor variable changes to string with values of 1, 2, and 3.Before applying as.numeric function, I cannot take the mean of the factor variable. However, since it is a three-level factor variables, it can be interpreted as reasonable numeric value and thus can be calculated for mean.


